si: code and prose exploring Spatial Interaction models

### 2022-04-16 README.qmd
Change name of example datasets, close #2

```{r installation}
remotes::install_github("robinlovelace/si")
```

@@

```{r distance}
library(si)
od = si_to_od(origins = zones, destinations = zones, max_dist = 5000)
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```

>>>>

```r
remotes::install_github("robinlovelace/si")
```

@@

```{r distance}
library(si)
od = si_to_od(
  origins = si_zones,
  destinations = si_zones,
  max_dist = 5000
  )
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```
